It is recorded that there are more than 53815 items was traded in the period
11/2021--06/2022, and more than half of them --- 68,69\% --- are personal data
, including full name, \acrlong{dob}, \acrlong{ssn}, \acrlong{dl}, \acrlong{cs},
etc. The second
most traded product type is username and password pair for accessing online
services of banking, entertaining, and shopping. Both aforementioned product
categories are traded at unexpectedly low cost, less than 15 USD for an entry or
a set of data. The cheapest item are sold at only 0.2 USD for an entry of personal
data (\emph{full name + date of birth + social security number}). Those personal
information is highly possible that are stolen from major data breaches. Through
those data breaches, an attacker gains a set of intial dataset of credential data
that is utilized to trick people trustfully provide more their sensitive data or
access to their online accounts of essential services such as banking or social
security. The consequences of identity theft have been documented thoroughly.
For example, identity thieves can use stolen \acrshort{ssn}s to apply for more
credit and then do not pay the bills, damaging credit of compromised identities~\cite{web:identity_theft}.
As there is a increasing number of data breaches over time, resulting the personal
data is traded at low-cost and highly available, the negative consequences can impact
a wider range of people.

Besides stolen sensitive data, Database marketplace also provides illicit services
such as faking passports, and other identity documents. Ranging from 20 to 1200 USD,
you can order a customized identity document. In addition to an affordable price range,
those services are coveniently traded through the Tor-based marketplace, Database in
this study. The marketplace supports functions, including chatting with sellers, 
searching keywords, and refunding orders, as the normal marketplace, e.g, Ebay.

In conclusion, Database marketplace provides a wide range of affordable products which
can be utilized to do illegal activities. Moreover, these products are highly
available and sold at reasonable prices; thus, an increasing number of criminal
acts related to identity theft, bank withdrawing, or credit abusing has been
observed. Those acts have rocketing impact on victims, not only financial but
also mental health.
